A robust framework for variable extrusion width concentric toolpath generation

### 2019-07-08 10_applications.tex
lil redo of validation and of applications

\subsection{Variable thickness microstructures}
show the effect of the planned toolpath on the performance of varying thickness microstructures

Implement varying width for infill patterns in Cura?

>>>>

\subsection{Thin parts}
\begin{itemize}
\item Casings (e.g. for electronics)
\item Prototypes for blowmold parts or sheet metal parts etc.
\item Miniature models, architectural models
\item Microstructures
\item Lithophanes
\end{itemize}

show the effect of the planned toolpath on the performance of varying thickness microstructures

\subsection{Widening}
Regions where the model is narrower than the nozzle size can be printed with a bead width larger than the model thickness.

### 2019-07-08 6_validation.tex
outline of other sections
lil redo of validation and of applications

\section{Validation}
Render toolpaths and calculate percentage of covered volume.

@@

>>>>

\section{Validation}

\subsection{Strategies}
We can emulate a variety of toolpath generation strategies by applying various beading strategies to our framework.

\paragraph{Naive Strategy}

\paragraph{Constant bead count}
Emulates \cite{Ding2016a}

\paragraph{Deviation at middle}
Emulates \cite{Jin2017}

\paragraph{Only outer bead}
Emulates \cite{Moesen2011}

\paragraph{Distributed strategy}
Distribute the overfill or underfill which would happen using a naive strategy over all beads.
This maximizes robustness and minimizes narrow beads qhich are difficult to print.

\paragraph{Combined strategy}
\Cref{wedge_and_infill} shows a combined toolpath strategy.

\begin{figure}
\centering
\includegraphics[width=.99\columnwidth]{sources/method/wedge_and_infill.pdf}
\caption{Use single and double wall lines in regions where the infill would be too thin.}
\label{wedge_and_infill}
\end{figure}

\subsection{Filling accuracy}
Render toolpaths and calculate percentage of covered volume.

@@

Show results for different settings.

Also render with nozzle size as minimal width and use middle of toolpaths instead of middle of beads.

Take same examples as Moessen: grids of triangular holes and circular holes.
Also use examples of Jin and Kao.

Use example layers of a typical object with thin walls: electronics casing.
